A meta-analysis of mental rotation ability in the first years of life

### 2022-04-21 code/analysis.Rmd
Correct formula for `sd_av`

    # Add difference between condition means
    mean_diff = case_when(
      !is.na(mean_diff) ~ mean_diff,
      TRUE ~ mean_novel - mean_familiar
    ),
    # Add d_z from paired t test of condition means (Rosenthal, 1991)
    d_z_t = t / sqrt(sample_size),
    # Add d_z from ANOVA F value via conversion to a t value
    d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
    # Add d_z from mean and standard deviation of the difference
    d_z_diff = mean_diff / sd_diff,
    # Add d_av from mean difference and standard devations (assumes r = 0.5)
    # (Cumming, 2012)
    sd_av = (sd_novel + sd_familiar) / 2,
    d_av = mean_diff / sd_av,
    # Add d from one-sample t test of novelty preference scores
    d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,

>>>>

    # Add difference between condition means
    mean_diff = case_when(
      !is.na(mean_diff) ~ mean_diff,
      TRUE ~ mean_novel - mean_familiar
    ),
    # Add d_z from paired t test of condition means (Rosenthal, 1991)
    d_z_t = t / sqrt(sample_size),
    # Add d_z from ANOVA F value via conversion to a t value
    d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
    # Add d_z from mean and standard deviation of the difference
    d_z_diff = mean_diff / sd_diff,
    # Add d_av from mean difference and standard devations
    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
    sd_av = sqrt((sd_novel^2 + sd_familiar^2) / 2),
    d_av = mean_diff / sd_av,
    # Add d from one-sample t test of novelty preference scores
    d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,
